Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-17 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
引用图表

\begin{figure}[htbp]
\centering
%\subfigure{\includegraphics[width=0.2\textwidth]{images/x.jpg}} \qquad
%\subfigure{\includegraphics[width=0.2\textwidth]{images/z.jpg}}
\includegraphics[width=0.48\textwidth]{images/1_v4.pdf}
\caption{Our approach generates the universal perturbations which can be used to attack the Siamese tracker on any video in a targeted manner. Our approach allows perturbing a new video to come at no additional cost except the mere addition and pasting operations -- and not require gradient optimisation or network inference.}
\end{figure}

@@

In this paper, we make the first attempt in finding the video-agnostic perturbations that fool state-of-the-art Siamese trackers in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal imperceptible perturbation to the template image and pasting a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory, so that tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition and pasting operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} datasets demonstrate the effectiveness and efficiency of our approach.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{images/network_v4.png}
\caption{The pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target.}
\end{figure}

@@

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target.
Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require solving an optimisation problem/gradient computation.

@@

GOT-10k \cite{GOT-10k} is a recent large-scale high-diversity dataset. There is no overlap in object classes between the train/val/test splits, promoting the importance of generalization to unseen object classes.
%Because we need to use the real ground truth to generate the fake ground truth, and the fake ground truth is not available on test set, so we use the val set.
%The evaluation metric is AO and Success rate, which means ...
We use average overlap (AO) for evaluation.
The AO relative to $B^{fake}$ on the adversarial videos is 0.818, which demonstrates that the generated universal perturbations can mislead the track to follow a specified trajectory.
%On GOT-10k Val set, the AO relative to $B^{gt}$ on the clean videos is 0.760. The AO relative to $B^{gt}$ on the adversarial videos is 0.023.

>>>>

\begin{figure}[htbp]
\centering
%\subfigure{\includegraphics[width=0.2\textwidth]{images/x.jpg}} \qquad
%\subfigure{\includegraphics[width=0.2\textwidth]{images/z.jpg}}
\includegraphics[width=0.48\textwidth]{images/1_v4.pdf}
\caption{Our approach generates the universal perturbations which can be used to attack the Siamese tracker on any video in a targeted manner. Our approach allows perturbing a new video to come at no additional cost except the mere addition and pasting operations -- and not require gradient optimisation or network inference.}
\label{fig:1}
\end{figure}

@@

In this paper, we make the first attempt in finding the video-agnostic perturbations that fool state-of-the-art Siamese trackers in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal imperceptible perturbation to the template image and pasting a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory, so that tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition and pasting operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} datasets demonstrate the effectiveness and efficiency of our approach (see Figure \ref{fig:1}).

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{images/network_v4.png}
\caption{The pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target.}
\label{fig:net}
\end{figure}

@@

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target (see Figure \ref{fig:net}).
Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require solving an optimisation problem/gradient computation.

@@

GOT-10k \cite{GOT-10k} is a recent large-scale high-diversity dataset. There is no overlap in object classes between the train/val/test splits, promoting the importance of generalization to unseen object classes.
%Because we need to use the real ground truth to generate the fake ground truth, and the fake ground truth is not available on test set, so we use the val set.
%The evaluation metric is AO and Success rate, which means ...
We use average overlap (AO) for evaluation.
The AO relative to $B^{fake}$ on the adversarial videos is 0.818, which demonstrates that the generated universal perturbations can mislead the track to follow a specified trajectory (see Figure \ref{fig:vis}).
%On GOT-10k Val set, the AO relative to $B^{gt}$ on the clean videos is 0.760. The AO relative to $B^{gt}$ on the adversarial videos is 0.023.
